### 2015-01-11 paper/Content/02research.tex
Merge
Intents

\section{MVP applied to Android Apps}

\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.

@@

>>>>

\section{Research}
\label{sec:research}

% MVP applied to Android Apps

\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
\todo[inline]{Change me}

@@

\textbf{Intent}: Intents are objects used for communication with the \emph{Android} system. An example would be the start of an activity: an intent must be created including some information to identify, which activity should be started. The intent will be handed over to the \emph{Android} system, which will create and start a corresponding activity. In the official SDK documentation, an intent is defined as \enquote{a messaging object you can use to request an action from another app component} \cite{SDKIntents}.

### 2015-01-11 paper/Content/solution.tex
Intents

As mentioned above, the basic building blocks of an Android application are \emph{Activities} and \emph{Fragments}. Applying MVP to an Android application therefore means to put attention on those components.

@@

\todo[inline]{Maybe add something about Intents here}

This answers RQ3, showing that MVP can be applied to an Android application considering the \emph{Activity} and \emph{Fragment} building blocks.

>>>>

As mentioned above, the basic building blocks of an Android application are \emph{Activities}, \emph{Fragments} and \emph{Intents}. Applying MVP to an Android application therefore means to put attention on those components.

@@

As \emph{Intents} are received by the activity object, they can be handled like any other view-related action (e.g. a click on a button). Whenever an intent was received by the activity, a corresponding action on the presenter object is executed -- nothing else. When it comes to creating intents, e.g. for switching to another activity, things get a bit more complicated. One would typically do such action inside the presenter, but intents require to be sent from a specific context, which can either be an activity or the application itself. This means that for creating an intent, the presenter must either address the main application object directly or go back to the activity and let the activity send the intent.

This answers RQ3, showing that MVP can be applied to an Android application considering the \emph{Activity}, \emph{Fragment} and \emph{Intent} building blocks.
